A Switching Planner for Combined Task and Observation Planning

### 2010-11-28 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/prop-dtp.tex
Few fixes requested by Moritz

We describe the partially observable propositional probabilistic
planning problem, with costs and rewards. We model a process
state $\state$ as the set of propositions that are true of the
state. Notationally, we have $\state \subseteq
\props$. The underlying process
dynamics are modelled in terms of a finite set of {\em probabilistic
STRIPS operators}~\cite{boutilier:1996} $\stochActions$ over
state-characterising propositions $\propositions$.
%%
Notationally, we say an action $\stochAction \in \stochActions$ is
applicable if its precondition $\poss(\stochAction)$, a set of
propositions, are satisfied in the current state -- i.e., $\poss(\stochAction) \subseteq
\state$. We denote $\mu_{\stochAction}(\detAction_i)$ the probability that
nature chooses a deterministic STRIPS effect $\detAct_i$, and for
all \stochAction\ we require
$\sum_{\detAction_i \in \detActions(\stochAction)}
\mu_{\stochAction}(\detAction_i) = 1$.

@@

We are concerned with problems that feature partial
observability. Although we could invoke {\em extended probabilistic
STRIPS operators}~\cite{rintanen:01} to model actions and observations
propositionally, we find it convenient for our presentation to clearly
separate sensing and action. Therefore, we suppose a POMDP has a
perceptual model given in terms of a finite set of stochastic {\em
senses} $\stochSenses$, deterministic sensing outcomes $\detSenses$,
and perceptual propositions $\percepts$, called {\em percepts}. In
detail, we take an observation $\observ$ to be a set of percepts
$\observ \subseteq \percepts$, and denote \observations\ the set of
reachable observations. The underlying state of the process cannot be
observed directly, rather, senses $\stochSense \in \stochSenses$
effect an observation $\observ \in
\observations$ that informs what should be believed about the state a
process is in. In detail, if $\action$ is applied effecting a
transition to a successor state $\state'$, then an observation occurs
according to the active senses $\stochSenses(\stochAction, \state')
\subseteq \stochSenses$. A sense $\stochSense$ is active, written
$\stochSense \in \stochSenses(\stochAction, \state')$, if the senses'
action-precondition, $\poss_\stochActions(\stochSense)$, is equal to
$\stochAction$, and the state-precondition $\poss_\states(\stochSense)
\subseteq \propositions$ is satisfied by the state $\state'$; In the
usual sense that $\poss_\states(\stochSense) \subseteq \state'$.
%%
When a sense is active, nature must choose exactly one outcome amongst
a small set of deterministic choices $\detSenses(\stochSense)
\equiv \{\detSense_1, \ldots, \detSense_k \}$, so that for each
$i$ we have $\detSense_i \subseteq \percepts$. The probability of
the $i^{th}$ element being chosen is given by
$\psi_{\stochSense}(\detSense_i)$, where $\sum_{\detSense_i \in
\detSenses(\stochSense)} \psi_{\stochSense}(\detSense_i) =
1$. The observation received by the agent corresponds to the union of
perceptual propositions from chosen elements of active
senses.

>>>>

We describe the partially observable propositional probabilistic
planning problem, with costs and rewards. We model a process
state $\state$ as the set of propositions that are true of the
state. Notationally, we have $\state \subseteq
\props$. The underlying process
dynamics are modelled in terms of a finite set of {\em probabilistic
STRIPS operators}~\cite{boutilier:1996} $\stochActions$ over
state-characterising propositions $\propositions$.
%%
We say an action $\stochAction \in \stochActions$ is
applicable if its precondition $\poss(\stochAction)$, a set of
propositions, are satisfied in the current state -- i.e., $\poss(\stochAction) \subseteq
\state$. We denote $\mu_{\stochAction}(\detAction_i)$ the probability that
nature chooses a deterministic STRIPS effect $\detAct_i$, and for
all \stochAction\ we require
$\sum_{\detAction_i \in \detActions(\stochAction)}
\mu_{\stochAction}(\detAction_i) = 1$.

@@

We are concerned with problems that feature partial
observability. Although we could invoke {\em extended probabilistic
STRIPS operators}~\cite{rintanen:01} to model actions and observations
propositionally, we find it convenient for our presentation to clearly
separate sensing and action. Therefore, we suppose a POMDP has a
perceptual model given in terms of a finite set of stochastic {\em
senses} $\stochSenses$, deterministic sensing outcomes $\detSenses$,
and perceptual propositions $\percepts$, called {\em percepts}. In
detail, we take an observation $\observ$ to be a set of percepts
$\observ \subseteq \percepts$, and denote \observations\ the set of
reachable observations. The underlying state of the process cannot be
observed directly, rather, senses $\stochSense \in \stochSenses$
effect an observation $\observ \in
\observations$ that informs what should be believed about the state a
process is in. If $\action$ is applied effecting a
transition to a successor state $\state'$, then an observation occurs
according to the active senses $\stochSenses(\stochAction, \state')
\subseteq \stochSenses$. A sense $\stochSense$ is active, written
$\stochSense \in \stochSenses(\stochAction, \state')$, if the senses'
action-precondition, $\poss_\stochActions(\stochSense)$, is equal to
$\stochAction$, and the state-precondition $\poss_\states(\stochSense)
\subseteq \propositions$ is satisfied by the state $\state'$; In the
usual sense that $\poss_\states(\stochSense) \subseteq \state'$.
%%
When a sense is active, nature must choose exactly one outcome amongst
a small set of deterministic choices $\detSenses(\stochSense)
\equiv \{\detSense_1, \ldots, \detSense_k \}$, so that for each
$i$ we have $\detSense_i \subseteq \percepts$. The probability of
the $i^{th}$ element being chosen is given by
$\psi_{\stochSense}(\detSense_i)$, where $\sum_{\detSense_i \in
\detSenses(\stochSense)} \psi_{\stochSense}(\detSense_i) =
1$. The observation received by the agent corresponds to the union of
perceptual propositions from the chosen elements of active
senses.
